NIRCam Faint and Bright Flux Calibration Plan

### 2018-01-23 ms.tex
Per Ralph Bohlin's comments, I added a table of MSX stars for reference.

\begin{figure*}[!t]
\centering
\subfloat[NGC 2420]{
	\includegraphics[width=0.5\textwidth]{sources_ngc2420.png}
	\label{fig:cmdNGC6811}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.5\textwidth]{sources_ngc2506.png}
	\label{fig:cmdNGC2506}
	}
\\
\subfloat[NGC 6811]{
	\includegraphics[width=0.5\textwidth]{sources_ngc6811.png}
	\label{fig:cmdNGC6811}
	}
	\caption{Color-magnitudes of the three clusters.
	The main sequence in each cluster was fit with a polynomial and then three priority levels were chosen for follow-up spectroscopy.
	The first priority targets were near-solar $g-r$ or B-V colors ($\pm 0.04, 0.03, 0.05$) that were within $\pm$4\arcmin\ of the cluster center (to concentrate in the NIRCam field of view).
	The second priority were near-solar $g-r$ or B-V colors but with a wider field of view (1$\degree$) to include G2~V stars that could be observed with larger dithers.
	Thirdly, any remaining main sequence stars that were within the 1$\degree$ hectospec field of view with reasonable signal to noise were selected to allow for errors in photometric color predictions and enable star cluster science at the main sequence turnoff point.}
	\label{fig:cmdPS}
\end{figure*}

@@

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black, for which the thermal and emissive properties were well understood.
Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event as the reference sphere.

@@

\begin{table}[!b]
\centering
\caption{Example Stars for Each Calibrator Step.}\label{tab:stepStars}
\begin{tabular}{lrrr}
\hline \hline
Step	(s)	& Source						& Spectral Type	& $K_\mathrm{src}$\tablenotemark{a}	\\
\hline \hline
1		& $\alpha$ Cen (Sirius)			& A1 V 			& -1.35		\\
1		& $\gamma$ Dra (Eltanin)			& K5 III 			& -1.35		\\
1		& $\alpha$ Lyr (Vega)			& A0 V 			& 0.13		\\
2 - 3		& HD 37962					& G2 V			& 6.27	  	\\
2 - 3		& HD 38949					& G1 V			& 6.44	  	\\
4 - 6		& 07:38:17.1 +21:36:22 (NGC 2420)	& G2 V			& 15.6 		\\
\hline
\end{tabular}
\tablenotetext{a}{NOTE, these magnitudes from Simbad may have up to 5\% systematics for steps 1-3..}
\vspace{0.05in} f
\end{table}

@@

Table \ref{tab:conversionStep} shows the saturation limits for each mode as well as the

@@

Observing the MSX flux standards (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}\footnote{https://github.com/JarronL/pynrc.git}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of $-$4.0 for an A1 V type star (Sirius is A1 V with K=$-$1.35) and $-$3.7 for an M3 III (Gacrux is $-$3.12).
This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.

@@

\subsubsection{Clocking Issues for Small Subarrays}

Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
Jarron explained further on April 24, 2017.
This is a known bug in the ASIC micro-code that can affect the frame times of small subarrays.
The bug creates extra line overheads on small subarrays.
For example, for a 32$\times$32 subarray, there are sometimes 2 line overheads and sometimes 3 line overheads about $\sim$40/60 \% of the time.
Tony Magoncelli has found a way to deterministically predict when these extra frame times will occur.
However, JWST will not produce enough data in flight to deterministically predict when the extra frame times occur so you'd have to average many frames together.
For a 64$\times$ 64 subarray, there are almost always 2 line overheads.
At a rate of about 5/8000 frames of test data, there were 3 line overheads.
So, in the worst case unlucky scenario with 64$\times$64 subarray data in RAPID mode with 2 groups up the ramp, there could be an extra 1/64 or 1.6 \% increase in the slope due to the ASIC micro code.
Given that 64$\times$64 frame time is only 0.05 s long, you could easily include hundreds of frames to average out the frame time issue with almost no change in efficiency since JWST acquisition, exposure and dithering overheads would be a much larger fraction of the time.
I would estimate this would have less than 0.01\% of an effect on flux calibration.

>>>>

\begin{figure*}[!t]
\centering
\subfloat[NGC 2420]{
	\includegraphics[width=0.5\textwidth]{sources_ngc2420.png}
	\label{fig:cmdNGC2420}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.5\textwidth]{sources_ngc2506.png}
	\label{fig:cmdNGC2506}
	}
\\
\subfloat[NGC 6811]{
	\includegraphics[width=0.5\textwidth]{sources_ngc6811.png}
	\label{fig:cmdNGC6811}
	}
	\caption{Color-magnitudes of the three clusters.
	The main sequence in each cluster was fit with a polynomial and then three priority levels were chosen for follow-up spectroscopy.
	The first priority targets were near-solar $g-r$ or B-V colors ($\pm 0.04, 0.03, 0.05$) that were within $\pm$4\arcmin\ of the cluster center (to concentrate in the NIRCam field of view).
	The second priority were near-solar $g-r$ or B-V colors but with a wider field of view (1$\degree$) to include G2~V stars that could be observed with larger dithers.
	Thirdly, any remaining main sequence stars that were within the 1$\degree$ hectospec field of view with reasonable signal to noise were selected to allow for errors in photometric color predictions and enable star cluster science at the main sequence turnoff point.}
	\label{fig:cmdPS}
\end{figure*}

@@

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}, listed in Table \ref{tab:msxStars}) and step down in brightness to faint standards used in JWST calibration.
The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black, for which the thermal and emissive properties were well understood.
Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event as the reference sphere.

@@

\begin{table}[!b]
\centering
\caption{Example Stars for Each Calibrator Step.}\label{tab:stepStars}
\begin{tabular}{lrrr}
\hline \hline
Step	(s)	& Source						& Spectral Type	& $K_\mathrm{src}$\tablenotemark{a}	\\
\hline \hline
1		& $\alpha$ Cen (Sirius)			& A1 V 			& -1.35		\\
1		& $\gamma$ Dra (Eltanin)			& K5 III 			& -1.35		\\
1		& $\alpha$ Lyr (Vega)			& A0 V 			& 0.13		\\
2 - 3		& HD 37962					& G2 V			& 6.27	  	\\
2 - 3		& HD 38949					& G1 V			& 6.44	  	\\
4 - 6		& 07:38:17.1 +21:36:22 (NGC 2420)	& G2 V			& 15.6 		\\
\hline
\end{tabular}
\tablenotetext{a}{NOTE, these magnitudes from Simbad may have up to 5\% systematics for steps 1-3..}
\vspace{0.05in}
\end{table}

\begin{table}
\centering
\caption{MSX Calibrator Stars and Fluxes.}\label{tab:msxStars}
\begin{tabular}{cccccc}
Star Name & Common Name & Spectral Type & K mag\tablenotemark{a} & B$_1$  & B$_2$ \\
      & &  & & 10$^{-15}$ W/cm$^{-2}$ & 10$^{-15}$ W/cm$^{-2}$ \\
\hline \hline
$\alpha$ Boo & Arcturus & K1.5 III & -2.91 & 56.0 $\pm$ 0.4 & 87.3 $\pm$ 0.5 \\
$\alpha$ Tau & Aldebaran & K5+ III & -3.04 & 47.6 $\pm$ 0.3 & 74.2 $\pm$ 0.4 \\
$\alpha$ Lyr & Vega & A0 V & 0.13 & 3.33 $\pm$ 0.04 & 5.34 $\pm$ 0.05 \\
$\beta$ Gem & Pollux & K0 III & -1.11 & 9.55 $\pm$ 0.08 & 15.0 $\pm$ 0.1 \\
$\gamma$ Dra & Eltanin & K5 III & -1.35 & 11.2 $\pm$ 0.1 & 17.3 $\pm$ 0.2 \\
$\gamma$ Cru & Gacrux & M3.4 III & -3.12 & 63.1 $\pm$ 0.6 & 98.2 $\pm$ 0.9 \\
$\beta$ And & Mirach & M0 III & -1.87 & 18.3 $\pm$ 0.3 & 30.0 $\pm$ 0.5 \\
$\alpha$ Cma & Sirius & A1 V & -1.35 & 11.8 $\pm$ 0.1\tablenotemark{b}& 18.9 $\pm$ 0.2\tablenotemark{b} \\
\end{tabular}
\tablenotetext{a}{K Magnitudes from Simbad}
\tablenotetext{b}{Scaling the Vega fluxes by the assigned -1.36 Vega Magnitude of Sirius using Table 3 in \citet{price2004msxCal}.}
\end{table}

@@

Table \ref{tab:conversionSteps} shows the saturation limits for each mode as well as the time needed to achieve a SNR of 200.

@@

Observing the MSX flux standards (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}\footnote{https://github.com/JarronL/pynrc.git}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of $-$4.0 for an A1 V type star (Sirius is A1 V with K=$-$1.35) and $-$3.7 for an M3 III (Gacrux is $-$3.12).
This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
There are some difficulties and potential pitfalls when attempting a multi-step ladder, so we describe these below.

\subsubsection{Implementation}
The APT science nor engineering template permit dithered subarray imaging with a 64$\times$64 subarray through a neutral density filter.
This prohibits executing Step 1 in Cycle 1 observing.
It is possible that in Cycle 2, more modes will be implemented including dithered subarray 64$\times$64 subarray imaging with a neutral density filter in place.

\subsubsection{Difficulty in Obtaining Accuracy}
The goal of the flux calibration effort is to achieve 1\% absolute flux calibration so the it is important to keep this mind.
The sum total error of all the steps of the NIRCam flux ladder must contribute less than 1\% so if the 6 errors are independent, the each must incur less than 0.4\% error.
In the pessimistic case that the errors are correlated, each step should have less than 0.17\%.
So, a signal to noise of 600 would be desired for each step on the ladder.

@@

\subsubsection{Clocking Issues for Small Subarrays - now resolved}

Marcia and Jarron previously brought up up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
Jarron explained further on April 24, 2017.
This was a known bug in the ASIC micro-code that can affect the frame times of small subarrays.
The bug creates extra line overheads on small subarrays.
For example, for a 32$\times$32 subarray, there are sometimes 2 line overheads and sometimes 3 line overheads about $\sim$40/60 \% of the time.
Tony Magoncelli has found a way to deterministically predict when these extra frame times will occur.
However, JWST did not produce enough data in flight to deterministically predict when the extra frame times occur so you'd have to average many frames together.
For a 64$\times$ 64 subarray, there are almost always 2 line overheads.
At a rate of about 5/8000 frames of test data, there were 3 line overheads.
So, in the worst case unlucky scenario with 64$\times$64 subarray data in RAPID mode with 2 groups up the ramp, there could be an extra 1/64 or 1.6 \% increase in the slope due to the ASIC micro code.
Given that 64$\times$64 frame time is only 0.05 s long, you could easily include hundreds of frames to average out the frame time issue with almost no change in efficiency since JWST acquisition, exposure and dithering overheads would be a much larger fraction of the time.
Thus, this would have less than 0.01\% of an effect on flux calibration.
Fortunately, the ASIC microcode was updated to fix this problem so there is no deterministic predictable timing for all subarrays, which was confirmed by Jarron Leisenring.
